---
title: "Incendies Promethee"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(readr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyverse)
library(leaflet)
library(plotly)
library(knitr)
library(DT)
```

```{r load_data, include = FALSE}
incendies_cases <- read.csv(file = "C:/Users/JNebot/Desktop/PROJECTES-PACA/INCENDIES-PACA/Dashboard/list_inc.csv",
                           header =  TRUE,
                           sep = ',')
```

Intro Page
=======================================



Column {data-width=650} {.tabset}
-----------------------------------------------------------------------

### Chart A

```{r}

```

### Chart A1
```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

Data Page
=======================================

### Data Table

```{r}

datatable(incendies_cases, rownames = FALSE, extensions = 'Buttons', options = list(    dom = 'Bfrtip',    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')  ))

```

Second Page
================================================
Column {data-width=650} 
-----------------------------------------------------------------------

### Chart A

```{r}

```


Column {data-width=350}
-----------------------------------------------------------------------

### Nombre total de feus

```{r}

n_total_feu <- count(incendies_cases)

valueBox(n_total_feu,
         caption = "Nombre total de feus",
         icon = "fa-clock-o")
```

### Nombre Total feus <= 1m2
```{r}

n_total_feu_1 <- incendies_cases %>%
                 select(Surface.parcourue..m2.) %>%
                 filter(Surface.parcourue..m2. <= 1) %>%
                 nrow()

valueBox(n_total_feu_1,
         caption = "Nombre total de feus <= 1m2",
         icon = "fa-clock-o")
```

### Nombre Total feus > 1m2 et <=100m2
```{r}

n_total_feu_100 <- incendies_cases %>%
                   select(Surface.parcourue..m2.) %>%
                   filter(Surface.parcourue..m2. >1,
                          Surface.parcourue..m2.<= 100) %>%
                   nrow()

valueBox(n_total_feu_100,
         caption = "Nombre total de feus >1m2 et <= 100m2",
         icon = "fa-clock-o")
```

### Nombre Total feus > 100m2
```{r}

n_total_feu_big <- incendies_cases %>%
                   select(Surface.parcourue..m2.) %>%
                   filter(Surface.parcourue..m2. > 100) %>%
                   nrow()

valueBox(n_total_feu_big,
         caption = "Nombre total de feus >100m2",
         icon = "fa-clock-o")
```

### Chart B

```{r}

```

### Chart C

```{r}

```

Carte
================================================

### Carte des Feu

```{r}
leaflet() %>%
addTiles() # %>%
#addMarkers(lng = stations_df$longitude, lat = stations_df$latitude) 

```